\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2018-07-27 sections/coverpage.tex
Add affiliations to the coverpage

  \vspace{1.5 cm}
  Dileep Kishore, Gabriel Birzu, Zhenjun Hu, Charles DeLisi, Kirill Korolev, Daniel Segre\\
  \vspace{1cm}
  Department of XYZ,\\
  The University of ABC\\
  Department of ABC,\\
  XYZ University\\

>>>>

  \vspace{1.5 cm}
  Dileep Kishore\textsuperscript{1},
  Gabriel Birzu\textsuperscript{2},
  Zhenjun Hu\textsuperscript{1},
  Charles DeLisi\textsuperscript{1,3},
  Kirill Korolev\textsuperscript{1,2},
  Daniel Segre\textsuperscript{1,3,4}\\
  \vspace{1cm}
  \textsuperscript{1}Bioinformatics Program, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{2}Department of Physics, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{3}Department of Biomedical Engineering, Boston University, Boston, Massachusetts, USA\\
  \textsuperscript{4}Department of Biology, Boston University, Boston, Massachusetts, USA\\
